\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2022-04-17 jss/cubble-jss.tex
notes on package install and rendering

{\centering \includegraphics[width=1\linewidth]{figures/illu-matching}

@@

{\centering \includegraphics[width=1\linewidth,height=0.7\textheight]{figures/basic-manip}

@@

{\centering \includegraphics[width=1\linewidth]{figures/basic-agg}

@@

{\centering \includegraphics[width=1\linewidth]{figures/matching-map}

@@

{\centering \includegraphics[width=1\linewidth]{figures/matching}

>>>>

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-cubble/figures/illu-matching}

@@

{\centering \includegraphics[width=1\linewidth,height=0.7\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/basic-manip}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-cubble/figures/basic-agg}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-cubble/figures/matching-map}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-cubble/figures/matching}
